Supporting information

### 2019-08-19 supplementary_information.Rmd
Fix SI authorship

---
title: Supporting information
author:
  - >
    Alexey N. Shiklomanov,
    Elizabeth M. Cowdery,
    Michael Bahn,
    Chaeho Byun,
    Joseph Craine,
    Andrés Gonzalez-Melo,
    Steven Jansen,
    Nathan Kraft,
    Koen Kramer,
    Vanessa Minden,
    Ülo Niinemets,
    Yusuke Onoda,
    Enio Egon Sosinski,
    Nadejda A. Soudzilovskaia,
    Michael C. Dietze
output: pdf_document
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \renewcommand{\thetable}{S\arabic{table}}
  - \renewcommand{\thefigure}{S\arabic{figure}}
---

>>>>

---
title: Supporting information
author:
  - >
    Alexey N. Shiklomanov,
    Elizabeth M. Cowdery,
    Michael Bahn,
    Chaeho Byun,
    Joseph Craine,
    Andrés Gonzalez-Melo,
    Steven Jansen,
    Koen Kramer,
    Vanessa Minden,
    Ülo Niinemets,
    Yusuke Onoda,
    Enio Egon Sosinski,
    Nadejda A. Soudzilovskaia,
    Michael C. Dietze
output: pdf_document
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \renewcommand{\thetable}{S\arabic{table}}
  - \renewcommand{\thefigure}{S\arabic{figure}}
---
